\TheTitle

### 2016-04-26 linvis.tex
Cleaning up a bit
Editing Introduction

Maintainers of older versions of the Linux kernel (such as those used in embedded systems and mobile phones) must keep track of changes to the current version
of the current in order to determine what commits are relevant to their versions.
Due to the ratio of growth of the kernel (every year, between 50 and 70 thousand commits get added to it)
this process requires
sifting through thousands of
commits with tools that are unable to filter and effectively visualize projects at
the scale of the kernel. Tools like Gitk use a directed acyclic graph (DAG) model,
showing all commits and merges in chronological order by when the commit was
authored, and not by then it arrives in the official repository.

This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, and how each branch is
interacting.  
In large modular projects, like the Linux kernel, the DAG becomes a
mess of merges and commits (figure \ref{fig:gitk}) losing its visual meaning.  In
some cases, the Linux kernel is simply too large for the system to generate a
visualization (eg. Github provides a DAG view for many projects, but is unable to
display the visualization for projects as large as the Linux kernel (figure
\ref{fig:gitfail}).
Furthermore, Linux creates between 60 and 70k new commits every year and, according to our previous work \cite{German2015}, 
a commit takes a median of 30 days from the moment it is authored to the time it arrives to the official repository
This means that, if a person inspected the commits in this repository today, tomorrow it might contain  many more
commits that were authored long before. However, distinguishing these new commits is not trivial.

@@

One of the challenges with visualizing the arrival of commits to a repository is that
in Git, commits are immutable, and Git does not store the date that a commit was merged into another branch (including master).
To complicate the problem, the DAG points to the ancestors of a commit (a model necessary for the operation of Git), but developers 
would prefer to know the path that a commit followed to reach the master repository.
Hence, tracing the path that any commit followed to master would imply that for any given merge, it would be possible to know what commits were merged. A user could
inspect the commits that have arrived into master within a given time frame by simply checking which commits where merged during that time frame.

% \dmg{I am going to describe the method we used here... }

% German et al. recorded the metadata of every commit and merge in the Linux git
% repository starting in 2011 \cite{German2015}, including chronological data that is
% not stored by git. We are able to use this information to determine when a commit
% has been merged into the kernel, regardless of rebases preceding and proceeding that
% point in time. This information is then converted by a heuristic method, described
% by German, to generate sets of trees, which we use as our core model instead of
% using the DAG. Each tree is rooted by the top-level merge performed by Linus, which
% merges the branches or a set of commits into the kernel.

 The contributions of this paper are two. First, we describe a method to convert the DAG of the Linux repository into a tree (we call this the \emph{merge-tree of the
 repository}) that represents the path used by
 any commit to reach master. Second, 
 we present a method to inspect and visualize the history of merges in the  Linux project using the tree-model of the repository

These methods and visualizations have been implemented in a web-based
tool called \tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}. Our visualizations and tool provide information about the location of any given
commit in its respective merge-tree, the files edited, the modules edited, and the
commit message for a given commit or merge. \tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

\evan{pdfs are not included in the repository}
\begin{figure}[htbp]
  \centering
        \includegraphics[width=\columnwidth]{figures/events.pdf}
  \caption{Example of a sequence of events performed in different repositories. The horizontal axis represents time. Each horizontal section represents a
    different branch and/or repository. Each commit points to its ancestor.}
  \label{fig:repoEvents}
\end{figure}

@@

The results of this verification show that this heuristic detected no incorrect merges since 2013, two incorrect merges in 2012, and two in 2011. However, due
to fast-forward commits performed in Linus Torvalds repository, this heuristic breaks apart on Oct 15, 2009, and no longer works for older merges.

@@

% \dmg{I would remove the command line shell, and use the space for related work}

% We came up with two designs. We recognized that the structure of the repository was
% similar to the wide and shallow tree-structure of a file system. We began with a
% command-line shell interface. Then transitioned to a web-based tool where we looked
% beyond the file system structure. In this section, we describe the progression of
% our tool design, showing the benefits and drawbacks of each component.

% \subsection{Command-line Shell}

% Our initial intuition was to work with the commits and merges as directory trees
% where the commits are files and the merges are directories. There are many
% similarities between the tree structure of a file system and the tree structure of
% the repository. Both trees are generally shallow, but very wide. File systems have
% been studied for quite some time and there are many tools capable of visualizing and
% working with the file structure.

% The first tool we implemented was a small command-line shell (figure
% \ref{fig:shell}) that allows users to navigate through the commits and merges as one
% might navigate through files and directories. A user could navigate toward the
% leaves of the tree by using the \verb|cd| command followed by the commit ID of the
% next merge. The user could then navigate toward the root by issuing \verb|cd ../|
% as they would in a file system. Users can use \verb|ls| to view what commits and
% merges exist in the current working merge, then use \verb|cat| to view the log
% preview of a commit or \verb|more| to see the preview and how many lines were added
% and removed from the files in the commit.

% \begin{figure}
%         \centering
%         \includegraphics[width=0.47\textwidth]{figures/shell.png}
%         \caption{Shell Design}
%         \label{fig:shell}
% \end{figure}

% The shell does not meet our design goals. It only provides users with the ability to
% navigate from the root. If there is a commit or merge that they would like to
% investigate, they must find it with another tool and navigate through the tree to
% find it. Furthermore, it does not aggregate information in the merges, so users must
% manually aggregate the metadata. Another issue with this design is that it presents
% the users with the commit hashes, which are quite long and unpleasant to remember
% and type into the shell, but also do not provide any quick explanation of what the
% commit or merge may contain.

% \subsection{Web-based Tool}

To navigate and inspect the merge-tree view of the Kernel we
created a web-based tool called \tool. Creating a web-based
tool enables users to use the system without having to install additional software
or store a large database, making it more accessible, more easily maintainable, and
platform independent. 
% A web-based tool can leverage interactive means of
% navigation and provide better explanations of commits and merges than the
% command-line interface.
\tool uses the following mechanisms to reach our goals of better navigation and
better explanation of the changes.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
        \caption{Entire Reingold-Tilford Tree of a merge. This merge by Linus (a992bf836f9c3039a16f4bd068d161c86c6c3e2c) contains 1722 includes non-merge commits
          touching 239 modules and 1525 files.}
        \label{fig:zoomed_tree}
\end{figure}

@@

\evantodo{we need reference to bubble trees}

>>>>

Between 50 and 70 thousand commits are added to the Linux kernel per version
requiring maintainers of older versions of the Linux kernel to sift through
thousands of commits and merges with tools that are unable to filter and effectively
visualize projects at the scale of the kernel. Older versions of the kernel are used
in embedded systems and mobile phones; for security purposes, performance needs, and
changing hardware requirements, maintainers must be able to understand the changes
being made in the current version of the kernel in order to produce the necessary
patches for the older versions of the kernel. Tools like Gitk use a directed acyclic
graph (DAG) model of the repository, showing all commits and merges in chronological
order by when the commit was authored, not by when it arrived in the official Linux
repository.

This representation works in smaller projects; it enables users to see when changes
are made, when these changes are merged, how each branch is interacting, and the
point where a branch forks from the master branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits (figure
\ref{fig:gitk}) losing its visual meaning. In some cases, the Linux kernel is simply
too large for the system to generate a visualization; Github provides a DAG view for
many projects, but is unable to display the visualization for projects at the scale
of the Linux of the kernel (figure \ref{fig:gitfail}).  Between 60 and 70k new
commits are created for the Linux project every year; According to our previous
work\cite{German2015}, a commit takes a median of 30 days from the time it is
authored until it arrives in the official repository. The snapshot of the kernel
tomorrow may be different than the snapshot from today, containing new commits
authored in the past; distinguishing these new commits from the commits in the
snapshot from today is not trivial.

@@

One major challenge with visualizing the arrival of commits to a repository is that
Git does not store the date that a commit was merged into another branch (including
master). To complicate the problem, the DAG has reference to the ancestors of a
commit (a model necessary for the operation of Git), but developers would prefer
knowing the path a commit followed to reach the master repository. Tracing a path
that any commit followed to the master repository would imply that for any given
merge, it would be possible to know which commits were merged. A user could inspect
the commits that arrived into master within a given time-frame by checking which
commits were merged during that time-frame.

This paper makes two contributions; first, we describe a method of converting the
DAG of the Linux repository into a tree, or \emph{merge-tree} of the repository,
that represents the path used by a commit to reach master; second, we present a
method to inspect and visualize the history of merges in the Linux project using the
merge-tree model.

These methods and visualizations are implemented in a web-based tool called
\tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}.
Our visualizations and tool provide information about the location of any given
commit in its respective merge-tree, the files edited, the modules edited, and the
commit message for a given commit or merge. \tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

\begin{figure}[htbp]
        \centering
        \includegraphics[width=\columnwidth]{figures/events.pdf}
        \caption{Example of a sequence of events performed in different repositories. The horizontal axis represents time. Each horizontal section represents a
                different branch and/or repository. Each commit points to its ancestor.}
        \label{fig:repoEvents}
\end{figure}

@@

The results of this verification show that this heuristic detected no incorrect merges since 2013, two incorrect merges in 2012, and two in 2011. However, this
heuristic breaks apart on Oct 15, 2009 due
to the presence of so-called foxtrot commits that confound the true Master branch of a repository \footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and no longer works for older merges.

@@

To navigate and inspect the merge-tree view of the Kernel we created a web-based
tool called \tool. Creating a web-based tool enables users to use the system without
having to install additional software or store a large database, making it more
accessible, more easily maintainable, and platform independent. \tool uses the
following mechanisms to reach our goals of better navigation and better explanation
of the changes.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
        \caption{Entire Reingold-Tilford Tree of a merge. This merge by Linus (73287a43cc79ca06629a88d1a199cd283f42456a) contains 1722 includes non-merge commits
                touching 239 modules and 1525 files.}
        \label{fig:zoomed_tree}
\end{figure}

@@
